analysis

### 2024-12-06 analysis.qmd
created the school.funding.cat variable

```{r}
#Need to convert school funding adequacy imputed values to school funding categorical variable before using in models
# imputated data has 5 dataframes within a list, need to run a loop for all five datasets to create a categorical variable for each set. 
```

@@

with(sub.imp, glm(School.Funding.Cat ~ Residential.Segregation.Index + Median.Household.Income + Median.Prop.Tax, family="binomial"))

>>>>

```{r}
#Need to convert school funding adequacy imputed values to school funding categorical variable before using in models
# imputated data has 5 dataframes within a list, need to run a loop for all five datasets to create a categorical variable for each set.

# Create a function to classify school funding adequacy into categories
# Create a function to classify school funding adequacy into categories
categorize_school_funding <- function(x) {
  ifelse(x < 50, "Low",
         ifelse(x < 75, "Medium", "High"))
}

# Create an empty list to store the categorical variables
sub.imp$imp$School.Funding.Cat <- list()

# Loop over the 5 imputations
for (i in 1:5) {
  # Access the i-th set of imputed values for School.Funding.Adequacy
  adequacy_values <- sub.imp$imp$School.Funding.Adequacy[, i]

  # Apply the categorization function
  sub.imp$imp$School.Funding.Cat[[i]] <- categorize_school_funding(adequacy_values)
}

# Verify the new categorical variables
str(sub.imp$imp$School.Funding.Cat)

@@

```{r}
with(sub.imp, lmod, family="binomial")
